---
title: "pier"
#author: "mj"
#date: "10 May 2016"
output: 
    html_document:
        keep_md: true
---

The `pier` package (pronounced pie-r) is a wrapper, or [htmlwidget](http://www.htmlwidgets.org/), for the [d3pie](http://d3pie.org/) javascript library by [Benjamin Keen](https://github.com/benkeen). If you are just wanting to generate a pie chart the d3pie website has a fantastic [generator](http://d3pie.org/#generator) that will create the code that you need. If you are wanting create a chart using [R](https://www.r-project.org/) for embedding in a Rmarkdown document or Shiny App, then you are in the right place.  

The `d3pie` library is very versatile and includes a lot of options. Currently this package only wraps the [configuration object](http://d3pie.org/#docs-configuration). Even with this current limitation a wide range of options are available. 

Currently the intention is to wrap the entire [`d3pie` api](http://d3pie.org/#docs-api). 


## Installation

You probably already guesssed this bit.

```{r install, eval=FALSE}

devtools::install_github("mrjoh3/pier")

```


## Usage

The `pier` package is intended to be as simple and lightweight as possible. As a starting point the data input must be a `data.frame` with three required columns: `label`, `value` and `color`. From this point most of the defaults from `d3pie` are carried over.  

```{r data, warning=FALSE, message=FALSE, fig.align='center'}

library(pier)

data <- data.frame(label = c('Environment','Education','Business','Community'),
                   value = c(104,19,638,1250),
                   color = RColorBrewer::brewer.pal(4, 'Spectral'))

pier(data)

```


## Piping

The package also imports the [migrittr](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html) piping function (`%>%`) to simplify syntax.

```{r pipe, fig.align='center'}

data %>%
    pier() %>%
    pie.header('My New Header')

```

