---
title: "pier"
#author: "mj"
#date: "10 May 2016"
output: 
    rmarkdown::github_document
---
[![DOI](https://zenodo.org/badge/56191948.svg)](https://zenodo.org/badge/latestdoi/56191948)
[![Build Status](https://travis-ci.org/mrjoh3/pier.svg?branch=master)](https://travis-ci.org/mrjoh3/pier)
[![codecov](https://codecov.io/gh/mrjoh3/pier/branch/master/graph/badge.svg)](https://codecov.io/gh/mrjoh3/pier)


The `pier` package (pronounced pie-r) is a wrapper, or [htmlwidget](http://www.htmlwidgets.org/), for the [d3pie](http://d3pie.org/) javascript library by [Benjamin Keen](https://github.com/benkeen). If you are just wanting to generate a pie chart the d3pie website has a fantastic [generator](http://d3pie.org/#generator) that will create the code that you need. If you are wanting create a chart using [R](https://www.r-project.org/) for embedding in a Rmarkdown document or Shiny App, then you are in the right place.  

The `d3pie` library is very versatile and includes a lot of options. Currently this package only wraps the [configuration object](http://d3pie.org/#docs-configuration). Even with this current limitation a wide range of options are available. 

Currently the intention is to wrap the entire [d3pie](http://d3pie.org/#docs-api) api. 



## Installation

You probably already guesssed this bit.

```{r install, eval=FALSE}

devtools::install_github("mrjoh3/pier")

```


## Usage

The `pier` package is intended to be as simple and lightweight as possible. As a starting point the data input must be a `data.frame` with three required columns: `label`, `value` and `color`. From this point most of the defaults from `d3pie` are carried over. Note that all examples here have lost their interactivity. 

```{r data, warning=FALSE, message=FALSE, fig.align='center', fig.width=8}

library(pier)

data <- data.frame(label = c('Environment','Education','Business','Community'),
                   value = c(104,119,638,1250),
                   color = RColorBrewer::brewer.pal(4, 'Spectral'))

simple.pie <- pier(data)

```


```{r p1, echo=FALSE, eval=FALSE, fig.align='center', fig.width=6, fig.height=4}

simple.pie %>%
   pie.effects(load  = list(effect = 'none',
                            speed = 2000)) %>%
   pie.size(width = 600, height = 450)

```

<center>
<img src = "img/p1.png" />
</center>




## Advanced Usage

```{r advanced, fig.width=7, fig.align='center'}

advanced.pie <- data %>%
    pier() %>%
    pie.size(inner=70, outer=100, width = 600, height = 450) %>%
    pie.header(text='Segments', font='Impact', location='pie-center') %>%
    pie.subtitle(text='by Type') %>%
    pie.footer(text='Economic Segments using fake data.',
               location = 'bottom-left') %>%
    pie.tooltips()

```


```{r p2, echo=FALSE, eval=FALSE, fig.align='center', fig.width=6, fig.height=4}

advanced.pie %>%
   pie.effects(load  = list(effect = 'default',
                            speed = 1000))

```

<center>
<img src = "img/p2.png" />
</center> 

