---
title: "pier"
#author: "mj"
#date: "10 May 2016"
output: 
    html_document:
        keep_md: true
        self_contained: yes
---


```{r setup, echo=FALSE, warning=FALSE, message=FALSE}

library(webshot)

# thanks to https://rud.is/b/2016/03/04/capturing-wild-widgets-with-webshot/
capture_widget <- function(wdgt,
                           output=c("path", "markdown", "html", "inline"),
                           height, width,
                           png_render_path=tempfile(tmpdir = 'img', fileext=".png")) {
 
  wdgt_html_tf <- tempfile(fileext=".html")
 
  htmlwidgets::saveWidget(wdgt, wdgt_html_tf)
 
  webshot::webshot(url=sprintf("file://%s", wdgt_html_tf),
                   selector="#htmlwidget_container",
                   file=png_render_path,
                   vwidth=width, vheight=height,
                   delay = 2, expand = c(0,0,40,80))
 
  # done with HTML
  unlink(wdgt_html_tf)
 
  switch(match.arg(output, c("path", "markdown", "html", "inline")),
             `path`=png_render_path,
         `markdown`=sprintf("![widget](%s)", png_render_path),
             `html`=sprintf("<img src='%s'/>", png_render_path),
           `inline`=base64::img(png_render_path))
 
}
```

The `pier` package (pronounced pie-r) is a wrapper, or [htmlwidget](http://www.htmlwidgets.org/), for the [d3pie](http://d3pie.org/) javascript library by [Benjamin Keen](https://github.com/benkeen). If you are just wanting to generate a pie chart the d3pie website has a fantastic [generator](http://d3pie.org/#generator) that will create the code that you need. If you are wanting create a chart using [R](https://www.r-project.org/) for embedding in a Rmarkdown document or Shiny App, then you are in the right place.  

The `d3pie` library is very versatile and includes a lot of options. Currently this package only wraps the [configuration object](http://d3pie.org/#docs-configuration). Even with this current limitation a wide range of options are available. 

Currently the intention is to wrap the entire `[d3pie](http://d3pie.org/#docs-api)` api. 



## Installation

You probably already guesssed this bit.

```{r install, eval=FALSE}

devtools::install_github("mrjoh3/pier")

```


## Usage

The `pier` package is intended to be as simple and lightweight as possible. As a starting point the data input must be a `data.frame` with three required columns: `label`, `value` and `color`. From this point most of the defaults from `d3pie` are carried over. Note that all examples here has lost their interactivity. Static image were captured using the `[webshot](https://github.com/wch/webshot)` package; with thanks to [rud.is](https://rud.is/b/2016/03/04/capturing-wild-widgets-with-webshot/) for an example function  

```{r data, warning=FALSE, message=FALSE, fig.align='center'}

library(pier)

data <- data.frame(label = c('Environment','Education','Business','Community'),
                   value = c(104,19,638,1250),
                   color = RColorBrewer::brewer.pal(4, 'Spectral'))

simple.pie <- pier(data)

```

```{r data.webshot, echo=FALSE, warning=FALSE, message=FALSE, comment=NA, results='asis'}

cat(
    capture_widget(simple.pie,
                   'markdown', height=400, width=800)
)

```


## Piping

The package also imports the [migrittr](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html) piping function (`%>%`) to simplify syntax.

```{r pipe, warning=FALSE, message=FALSE, fig.align='center'}

piped.pie <- data %>%
                pier() %>%
                pie.header('My New Header')

```


```{r pipe.webshot, echo=FALSE, warning=FALSE, message=FALSE, comment=NA, results='asis'}

cat(
    capture_widget(piped.pie,
                   'markdown', height=400, width=800)
)

```
